Reconstructing the last known movements of one of Nature's giants

### 2018-02-15 manuscript/PNAS/blue-whale-ms.tex
Final PNAS submission edits

\section{Significance statement}
XXX 120 max

>>>>

\section{Significance statement}
Blue whales, the largest animals to have ever lived, are rare and enigmatic. 
We know little about their movements and life-history which hampers conservation efforts.
Here we investigate historical blue whale movements using stable isotopes from the baleen of the Natural History Museum London's blue whale ``Hope'', a female whale that stranded in 1891 at the height of industrial whaling.
We show that the whale spent at least two years in the sub-tropics as a juvenile, before beginning annual latitudinal migrations in the northeast Atlantic. 
The whale then likely became pregnant and raised a calf in sub-tropical waters before stranding.
Our results provide valuable insights into blue whale ecology, and also highlight museums as rich archives of individual-level behavioural information.
